Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-14 report/report.tex
Update introduction disposition

Applications:
    Navigating agents or pedestrian flows.
    Using a road network to creates an underlying navmesh
    This process is analytical and relies on the availablity and accurate representation of city maps.
    %TODO: (Parish Müller: Procedural modelin of cities)

Description of different levels of subdivision. What levels of subdivision are we looking at? Picture, ref to Todor's paper.

Viewpoints can range from modelling individual roads (find reference) and building facades (todor) to looking at entire city parcels and how they connect with each other (find reference).

Description of procedural modelling of cities (find reference).
Importing geodata from online databases and converting it to a 3D city representation.

At the base of this process is the procedural layout of road networks in 3D.

>>>>

Applications:
    Navigating agents or pedestrian flows.
    Using a road network to creates an underlying navmesh
    This process is analytical and relies on the availablity and accurate representation of city maps.
    (Parish Müller: Procedural modelin of cities)

Description of different levels of subdivision. What levels of subdivision are we looking at? Picture, ref to Todor's paper.
Viewpoints can range from modelling individual roads (find reference) and building facades (todor) to looking at entire city parcels and how they connect with each other (find reference).

Description of procedural modelling of cities
Importing geodata from online databases and converting it to a 3D city representation.
It would be labour intensive to recreate these .
Procedural models for city reproduction instead rely on programmatic solutions for converting map data to 3D road and building models, and composing them to a 3D world that the designer may continue to fine-tweak.
(Parish Müller, Procedural modeling of buildings)

At the base of this process is the procedural layout of road networks in 3D.
(Parish Müller, Procedural modeling of cities)
